### 2025-02-03 analysis/preprocessing.qmd
refactor(preprocessing): refactor model_class_id
rename random forests to tree-based methods and flexible discriminants to svm

```{r}
#| warning: false
#| echo: false
#| eval: true
# Set parameters and libraries
export_decision <- FALSE
verbose <- FALSE
require(here)
library(stringr)
library(tidyverse)
library(ggrepel)
library(ez)
library(ggdist)
```

@@

```{r}
#| eval: true
#| echo: false
# Classify techniques according Hastie, Tibshirani, Friedman (2008)
# https://www.sas.upenn.edu/~fdiebold/NoHesitations/BookAdvanced.pdf
#
metaMER_results$model_id <- tolower(metaMER_results$model_id)
metaMER_results$model_class_id <- 'Unclassified'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'lr|lm|pls|mlr|pcr|logistic regression|2d model full|pentagon|gaussian process regression|sparse bayesian regression|variational bayesian regression|logistic regression|lda|rda|regularized discriminant analysis|reguliarized discriminant analysis|linear discriminant|quadratic discriminant')] <- 'Linear Methods' # Class name from Elements of Stat.."
#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'logistic regression|lda|rda|regularized discriminant analysis|reguliarized discriminant analysis')] <- 'Linear Classification'
#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'mars|gam')]<-'Additive Trees and Related Methods' #
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rbf|gmm|local|polynomial|polygonal|knn|mars|gam')]<-'Kernel Smoothing, Additive and KNN'
#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'adaboost|gradient')]<-'Boosting'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'nn|gru|lstm|ltsm|long short term memory|rprop|mcan')]<-'Neural Nets'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'svm|svr|support vector regression|smoreg|smo ')]<-'Flexible Discriminants'
#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'knn')]<-'Prototype methods'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rf|extremely randomized tree regression|random forest|adaboost|gradient|tree|bag|boost')]<-'Random Forests'
#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rf')]<-'Ensemble Learning'

@@

tmp$dimension<-str_to_title(tmp$dimension)
tmp$model_class_id<-factor(tmp$model_class_id,
                           levels = c("Neural Nets","Flexible Discriminants", "Kernel Smoothing, Additive and KNN", "Random Forests","Linear Methods"),
                           labels = c("Neural\nNets","Flexible\nDiscriminants", "KS\n & KNN", "Random\nForests", "Linear\nMethods"))

@@

```{r}
#| echo: false
#| eval: false
C_studies$citekey <- factor(C_studies$citekey)
tmp <- drop_na(C_studies)
tmp$dimension<-str_to_title(tmp$dimension)
tmp$model_class_id<-factor(tmp$model_class_id,
                           levels = c("Neural Nets","Flexible Discriminants", "Kernel Smoothing, Additive and KNN", "Random Forests","Linear Methods"),
                           labels = c("Neural\nNets","Flexible\nDiscriminants", "KS\n & KNN", "Random\nForests", "Linear\nMethods"))

>>>>

```{r}
#| warning: false
#| echo: false
#| eval: true
# Set parameters and libraries
export_decision <- TRUE
verbose <- FALSE
require(here)
library(stringr)
library(tidyverse)
library(ggrepel)
library(ez)
library(ggdist)
```

@@

```{r}
#| eval: true
#| echo: false
# Classify techniques according Hastie, Tibshirani, Friedman (2008)
# https://www.sas.upenn.edu/~fdiebold/NoHesitations/BookAdvanced.pdf
#
metaMER_results$model_id <- tolower(metaMER_results$model_id)
metaMER_results$model_class_id <- 'Unclassified'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'lr|lm|pls|mlr|pcr|logistic regression|2d model full|pentagon|gaussian process regression|sparse bayesian regression|variational bayesian regression|logistic regression|lda|rda|regularized discriminant analysis|reguliarized discriminant analysis|linear discriminant|quadratic discriminant')] <- 'Linear Methods' # Class name from Elements of Stat.."
#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'logistic regression|lda|rda|regularized discriminant analysis|reguliarized discriminant analysis')] <- 'Linear Classification'
#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'mars|gam')]<-'Additive Trees and Related Methods' #
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rbf|gmm|local|polynomial|polygonal|knn|mars|gam')]<-'Kernel Smoothing, Additive and KNN'
#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'adaboost|gradient')]<-'Boosting'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'nn|gru|lstm|ltsm|long short term memory|rprop|mcan')]<-'Neural Nets'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'svm|svr|support vector regression|smoreg|smo ')]<-'Support Vector Machines'
#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'knn')]<-'Prototype methods'
metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rf|extremely randomized tree regression|random forest|adaboost|gradient|tree|bag|boost')]<-'Tree-based Methods'
#metaMER_results$model_class_id[str_detect(metaMER_results$model_id,'rf')]<-'Ensemble Learning'

@@

tmp$dimension<-str_to_title(tmp$dimension)
tmp$model_class_id<-factor(tmp$model_class_id,
                           levels = c("Neural Nets","Support Vector Machines", "Kernel Smoothing, Additive and KNN", "Tree-based Methods","Linear Methods"),
                           labels = c("Neural\nNets","Flexible\nDiscriminants", "KS\n & KNN", "Random\nForests", "Linear\nMethods"))

@@

```{r}
#| echo: false
#| eval: false
C_studies$citekey <- factor(C_studies$citekey)
tmp <- drop_na(C_studies)
tmp$dimension<-str_to_title(tmp$dimension)
tmp$model_class_id<-factor(tmp$model_class_id,
                           levels = c("Neural Nets","Support Vector Machines", "Kernel Smoothing, Additive and KNN", "Tree-based Methods","Linear Methods"),
                           labels = c("Neural\nNets","Flexible\nDiscriminants", "KS\n & KNN", "Random\nForests", "Linear\nMethods"))
